Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-02 causal-bandit/icml-2015/introduction.tex
Tweaks

In \S\ref{sec:simple-regret} we analyse a specific family of causal bandit problems that we call \emph{parallel bandit} problems in which $N$ factors affect the reward independently.
We propose a simple causal best arm identification algorithm (Algorithm~\ref{alg:simple}) for this problem and show it is optimal up to log factors (Theorems~\ref{thm:uq-simple} \& \ref{thm:lower}) with $\tilde{\Theta}(\sqrt{m/T})$ simple regret after $T$ rounds where $m$ depends on the casual model and may be much smaller than $N$.
In contrast, the best a bandit algorithm can do if the causal model is ignored is $\Omega(\sqrt{N/T})$.
This shows theoretically the value of our framework over the traditional bandit problem. 
Experiments in \S\ref{sec:experiments} further demonstrate the value of causal models in bandit problems.

Interventions and observations may have a complex relationship in the general causal model. 
However, in \S\ref{sec:simple-regret-general}, Theorem~\ref{thm:general-upper} shows how an importance-sampling based algorithm (Algorithm~\ref{alg:alloc}) can obtain non-trivial guarantees on simple regret.

>>>>

In \S\ref{sec:simple-regret} we analyse a specific family of causal bandit problems that we call \emph{parallel bandit} problems in which $N$ factors affect the reward independently.
We propose a simple causal best arm identification algorithm (Algorithm~\ref{alg:simple}) for this problem and show it is optimal up to log factors (Theorems~\ref{thm:uq-simple} \& \ref{thm:lower}) with $\tilde{\Theta}(\sqrt{m/T})$ simple regret after $T$ rounds where $m$ depends on the casual model and may be much smaller than $N$.
In contrast, the best a bandit algorithm can do if the causal model is ignored is $\Omega(\sqrt{N/T})$.
This shows theoretically the value of our framework over the traditional bandit problem. 
Experiments in \S\ref{sec:experiments} further demonstrate the value of causal models in bandit problems.
\todom{Mention cumulative regret?}

In the general casual model interventions and observations may have a complex relationship. 
However, in \S\ref{sec:simple-regret-general}, Theorem~\ref{thm:general-upper} shows how an importance-sampling based algorithm that exploits the causal graph (Algorithm~\ref{alg:alloc}) can obtain non-trivial guarantees on simple regret.
While this upper bound reduces to the one for parallel bandits, a matching lower bound for the general case is left as an open problem.
